---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CORproject

<!-- badges: start -->
<!-- badges: end -->

The goal of CORproject is to conduct simple statistical analyses based on a table based on tabular data in PNG format. The data is read using optical character recognition based on the [tesseract](https://github.com/tesseract-ocr/tesseract) package. The data is analyzed using an ANOVA. The analysis is summarized in a Rmd report.

## Installation

You can install the released version of CORproject from [GitHub](https://github.com/nrode/CORproject) with:

``` r
install_github("nrode/CORproject")
```

## Example

```{r example}
library(CORproject)

## Simulate data and save it as png
createpng(csvpath="data/FitnessExperimentalDesign_G60Final.csv", outputpng=here::here("data", "testnew.png"))

## Read the data using OCR and output a vector
data <- ocrpng(impagepath = here::here("data", "test.png"), n.col=NULL, lang="fra",  header=TRUE)

## Visualize data
graphe(csvpath=here::here("data", "fitness.csv"))

## Analyze data
analyse_stat(csvpath=here::here("data", "fitness.csv"))
```



